---
title: "Schedule"
author: "Christopher P. Kenaley"
date: "8/17/2020"
output: html_document
---

# Course schedule

## Week 1 (Aug 31—Sep 4)

```{r}
#Instal r codetools
#https://rstudio-education.github.io/hopr/starting.html]  

```


            Monday            Wednesday             Friday
--------   --------------   ----------------       ----------------
Read:      Course Welcome                
Watch:    
Deliver:                    Install R and Rstudio
--------   --------------   ----------------   ----------------

## Week 2 (Sep 7—11)

            Monday            Wednesday          Friday
--------   --------------   ----------------   ----------------
Read:      Course Welcome                   
Watch:    
Deliver:  
--------   --------------   ----------------   ----------------

## Week 3 (Sep 14–Sep 18)

            Monday            Wednesday          Friday
--------   --------------   ----------------   ----------------
Read:      Course Welcome                   
Watch:    
Deliver:  
--------   --------------   ----------------   ----------------

## Week 4 (Sep 21–Sep 25)

            Monday            Wednesday          Friday
--------   --------------   ----------------   ----------------
Read:      Course Welcome                   
Watch:    
Deliver:  
--------   --------------   ----------------   ----------------

## Week 5 (Sep 28–Oct 2)

            Monday            Wednesday          Friday
--------   --------------   ----------------   ----------------
Read:      Course Welcome                   
Watch:    
Deliver:  
--------   --------------   ----------------   ----------------

## Week 6 (Oct 5–9)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
## Week 7 (Oct 12–16)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 8 (Oct 19–23)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
## Week 9 (Oct 26–30)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 10 (Nov 2–6)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 11 (Nov 9–13)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 12 (Nov 16–20)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 12 (Nov 23–27)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 13 (Nov 30–Dec 4)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 14 (Dec 7–Dec 10)
### Monday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

### Wednesday
  + *Read:* 
  + *Watch:*
  + *Deliver:*
  
### Friday
  + *Read:* 
  + *Watch:*
  + *Deliver:*

## Week 15 (Sep 28–Oct 2)


```{r}
library(knitr)

sched <- data.frame(
  
  Week=c(1:16),
  Date=c("Aug31—Sep4","Sep7—11","Sep14—Sep18","Sep21-25","Sep20-Oct2","Oct5—9","Oct12—16","Oct19—16","Oct19—3","Oct26—30","Nov2—6","Nov9—13","Nov16—20","Nov23—27","Nov30—Dec4","Dec7—10"),
  Monday=""
  
  
)
write.csv(sched,"3140Sched.csv",row.names = F)
```
