---
title: "WCR 1"
author: "BIOL 3140"
date: "2023-09-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Fist begin by creating an R script name `Last_Fist_WRC1.R` [1 pt]

## Question 1

Complete the following steps, writing lines of code as needed.

1. Comment in "Question 1." [1 pt]

2. Make a vector containing the integers 1 through 10. Save the vector as a variable names `my_vec`. [1 pt]

3. Retrieve the 6th value of this vector. [1 pt]

4. Multiply this vector by 2. [1 pt]

5. Compute the `log` of each value. `?log` may help. [1 pt]


```{r include=F}
my_vec <- 1:10
log(my_vec)
```

## Question 2

Comment in "Question 2." Then, write a `for` loop that prints two times each value of `my_vec` appended with " is 2 times " and then the value, something like "2 is 2 times the value of 1". `?paste` may help. [4 pts]

```{r include=F}
for( i in my_vec){
  print(paste(2*i,"is 2 times",i))
}

```

## Submission

Submit your script via attachment by emailing it with the subject line "WRC1" to [kenaley@bc.edu](mailto:kenaley@bc.edu)

```{r eval=F,include=F}
library(rmarkdown)
library(fidelius)
pw <- "WCR1"
render("WCR_1.Rmd", html_password_protected(password=pw))

```
