---
title: "Final Project Report Feedback for `r params$team`"
output:  
  html_document:  
    theme: sandstone
    highlight: tango
    toc: true # adds a table of contents
    toc_float: true
    number_sections: FALSE
params:
  rigor_gr: NA
  tasks_gr: NA
  effort_gr: NA
  format_gr: NA
  analysis_gr: NA
  graphics_gr: NA
  writing_gr: NA
  sources_gr: NA
  rigor_fb: NA
  tasks_fb: NA
  effort_fb: NA
  format_fb: NA
  analysis_fb: NA
  graphics_fb: NA
  writing_fb: NA
  sources_fb: NA
  rigor_rub: NA
  tasks_rub: NA
  effort_rub: NA
  format_rub: NA
  analysis_rub: NA
  graphics_rub: NA
  writing_rub: NA
  sources_rub: NA
  module: NA
  team: NA
  general_fb: NA
          
---


```{r,echo=FALSE}
library(fontawesome)
```

<style>
div.green { background-color:#c7d1c0; border-radius: 5px; padding: 20px;}
</style>



------

## Tasks and Output 
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$tasks_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$tasks_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$tasks_gr)
```

</div>
</div>
</div>
<br>

------

## Scientific Rigor
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$rigor_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$rigor_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$rigor_gr)
```

</div>
</div>
</div>
<br>

------

## Effort and Engagement 
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$effort_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$effort_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$effort_gr)
```

</div>
</div>
</div>
<br>

------

## Report Format 
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$format_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$format_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$format_gr)
```

</div>
</div>
</div>
<br>

------

## Analysis and Code
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$analysis_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$analysis_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$analysis_gr)
```

</div>
</div>
</div>
<br>

------

## Graphics and Tables
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$graphics_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$graphics_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$graphics_gr)
```

</div>
</div>
</div>
<br>

------

## Writing and Style
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$writing_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$writing_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$writing_gr)
```

</div>
</div>
</div>
<br>

------

## Sources and References
<!-- Rubric -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Rubric Benchmark</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$sources_rub)
```

</div>
</div>
</div>
<br>

<!-- Feedback -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$sources_fb)
```

</div>
</div>
</div>
<br>

<!-- Grade -->

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$sources_gr)
```

</div>
</div>
</div>
<br>

------

## Overall Feedback and Grade

### General Feedback


<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Feedback</b></br>`r fa("sticky-note", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
cat(params$general_fb)
```

</div>
</div>
</div>
<br>



### Overall Grade

<div class = "green">
<div class="row">
  <div class="col-sm-2"><b>Grade</b></br>`r fa("check-square", fill = "black",height="50px")`</a> <!-- regular style --></div>
  <div class="col-sm-9">
  
```{r, results='asis', echo=FALSE}
grade <- sum(params$tasks_gr,params$rigor_gr,params$effort_gr,params$format_gr,params$analysis_gr,params$graphics_gr,params$writing_gr,params$sources_gr)


cat(grade)

```
</div>
</div>
</div>
<br>


