---
title: "Module 2: Data Wrangling"
subtitle: "Introduction to Tools of the Trade in Data Analysis"
author: "Dr. Christopher Kenaley"
institute: "Boston College"
date: "2026/9/14"
output:
  xaringan::moon_reader:
    css: ["default", "metropolis","slides.css"]
    lib_dir: libs
    nature:
      ratio: 16:9
---
# In class today 

```{r,echo=FALSE,message=FALSE,warning=F}
library(tidyverse)
library(kableExtra)
```

<!-- Add icon library -->
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/5.14.0/css/all.min.css">


.pull-left[
Today we'll ....

## Tidy data 

- Shape of data (long vs wide)

- Pivoting

- Joining and relational data

- Peak under the hood of Module Project 2

]

---
# Reminder 

.pull-left[


- Fill out peer [contribution form](https://docs.google.com/forms/d/e/1FAIpQLScmWkc_pszgLA_wj-d0gRGnM4EY3zPZeioqZTIs8FR6U8Nnug/viewform)!


]




---
#Shape of data

Wide: one row per sample; many columns for measurements

Iris ships in wide form (4 measurement columns + Species)

Pros: 

 - Easy to read raw values
 - Convenient for direct modeling/viz with specific columns

```{r}
head(iris, 6) 
```


---
#Shape of data

.pull-left[
Long: many rows per sample; fewer columns for measurements

Iris ships in long form (4 measurement in one column)

Pros: 

 - Tidy grammar enables grouped summaries, faceting, and tidy verbs (functions)
]

.pull-right[
```{r}
iris_long <- iris %>%
  pivot_longer(
    cols =Sepal.Length:Petal.Width 
  )

iris_long %>% head(6)
```
]

---
#Shape of data

.pull-left[

```{r, fig.height=4, fig.align='center'}
iris_long %>%
  ggplot(aes(x = name, y = value, fill = Species)) +
  geom_boxplot() +
  facet_grid(.~Species)+
  theme(axis.text.x = element_text(angle=60,hjust=1))
```
]

---
#Merging/joining data

Let's make some pH data

```{r, out.height="30%", fig.align='center'}
pH <- iris_long %>% 
  group_by(Species,name) %>% 
  reframe(pH=runif(1,5,8))
```

---
#Merging/joining data

join based on species

```{r, fig.height=4, fig.align='center'}

iris_long %>% 
  left_join(pH)
```
---
#Merging/joining data

join based on species and plotting

```{r, fig.height=4, fig.align='center'}

iris_long %>% 
  left_join(pH) %>%
  ggplot(aes(pH,value,col=name))+geom_point(alpha=0.1)+
  facet_grid(.~Species)
  
```






