---
title: "Module 1: The Basics"
subtitle: "Loading Data and Project Questions"
author: "Dr. Christopher Kenaley"
institute: "Boston College"
date: "2026/09/11"
output:
  xaringan::moon_reader:
    css: ["default", "metropolis","slides.css"]
    lib_dir: libs
    nature:
      ratio: 16:9
---

# Today we'll .....
```{r,echo=FALSE,message=FALSE,warning=F}
library(tidyverse)
library(kableExtra)
```

.pull-left[

- the pipe (`%>%`) and loading data

- open discussion Module Project 1
  


]


---

# Reminder 1

.pull-left[

- make personal repo

- make me (@ckenaley) a collaborator

- make it private!!
  

]


---


# Questions ahead of Module Project 1 

  - Due this Sunday 11:59 pm
  
  - Commit to assigned team repo
  
  - Each member commits own report (R script + figures)




---

# Loading data

- `readr` package has several handy functions.

- `read_csv()` most handy

```{r,fig.height=3,message=FALSE}
d <- read_csv("https://bcorgbio.github.io/class/data/coyote.csv")
head(d)
```

---

# Loading data


```{r,fig.height=3}
d%>%
  group_by(state)%>%
  dplyr::summarize(n=n())%>%
  ggplot(aes(x=state,y=n))+
  geom_bar(stat="identity")+
  coord_flip()
  
```



